Charity analysis

### 2022-07-18 Shiny/Test/Flexdashboard rows.Rmd
Commenting.

```{r setup, include=FALSE}
if (!require("pacman")) install.packages("pacman"); library(pacman)
p_load(shiny, tidyverse, scales, rvest, janitor, plotly, readxl,
       flexdashboard, MetBrewer, DT, fontawesome)
htmltools::tagList(fontawesome::fa_html_dependency())
```

@@

numericInput("start", label = "Start", value = 2002)
numericInput("end", label = "End", value = 2021)

@@

    # creating data frame from html file
    htmldata <- reactive({
      read_proff6(input$html$datapath,
                  as.character(input$start), as.character(input$end))
      })

@@

#---- Value Boxes ----------------------------------------------------------------

    # Creating value box
    KPI_admin <- reactive({exceldata() |> 
           mutate(
    KPI_admin =
      str_c(
        format(
        (expenses_administrative / expenses_program_services *100), digits = 3
        ), "%"
        )
  ) |> 
  filter(year == max(year)) |> 
  select(KPI_admin) |> 
  str_flatten()
    })

    output$KPI_box <- renderValueBox({
      valueBox(
        value = KPI_admin(),
        caption = "primary",
        color = "primary",
        icon = "fa-random"
      )
    })

@@

  # Creating fancy plotlyplot
    fancyplotly <- reactive({
      ggplotly(fancyplot())
    })
    output$fancyplotly <- renderPlotly(
      fancyplotly()
    )
})

@@

# Function to read Excel file
widen_excel <- function(file){
    read_excel(file) |> 
      mutate(
        Value = Value * 1000
      ) |> 
      unite(
        entry, c(Category, Name), sep = "_"
      ) |> 
      select(-`Sub-category`) |> 
      pivot_wider(names_from = entry, values_from = Value) |> 
      clean_names()
}
```

>>>>

```{r setup, include=FALSE}
# Packages using pacman
if (!require("pacman")) install.packages("pacman"); library(pacman)
p_load(shiny, tidyverse, scales, rvest, janitor, plotly, readxl,
       flexdashboard, MetBrewer, DT, fontawesome, htmltools)
# Using package fontawesome for fontawesome icons
htmltools::tagList(fontawesome::fa_html_dependency())
```

@@

# Year inputs
numericInput("start", label = "Start", value = 2002)
numericInput("end", label = "End", value = 2021)

@@

#---- Data frames --------------------------------------------------------------      
    # creating data frame from html file
    htmldata <- reactive({
      read_proff6(input$html$datapath,
                  as.character(input$start), as.character(input$end))
      })

@@

#---- Value Boxes --------------------------------------------------------------

    # Creating KPI_admin value
    KPI_admin <- reactive({exceldata() |> 
           mutate(
      KPI_admin =
        str_c(
         format(
          (expenses_administrative / expenses_program_services *100), digits = 3
          ), "%"
         )
      ) |> 
      filter(year == max(year)) |> 
       select(KPI_admin) |> 
        str_flatten()
         })

    # Creating the first value box
    output$KPI_box <- renderValueBox({
      valueBox(
        value = KPI_admin(),
        caption = "primary",
        color = "primary",
        icon = "fa-random"
        )
      })

@@

  # Creating fancy plotlyplot
    fancyplotly <- reactive({
      ggplotly(fancyplot())
    })
  # Creating fancy plotly output  
    output$fancyplotly <- renderPlotly(
      fancyplotly()
    )
})

@@

# Function to read Excel file
widen_excel <- function(file){
    read_excel(file) |> 
      mutate( # Changing values
        Value = Value * 1000
      ) |> 
      unite( # uniting Category and Name to deal with multiple 'Other'
        entry, c(Category, Name), sep = "_"
      ) |> 
      select(-`Sub-category`) |> # deleting Sub-category
    # pivoting
      pivot_wider(names_from = entry, values_from = Value) |> 
      clean_names() # cleaning names
}
```
